No-click browsing of large hierarchical data

### 2020-03-06 paper/HCC2020.save/paper.tex
IEEE用に修正

The simplest input device for Gear may be keyboards or buttons.
We tried using arrow keys on a PC, and it works fairly fine.
We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

We can use two arrow keys on a computer keyboard for using {\SC}.
It works fine, but Gear is not more useful than using many keys on a computer.
%
Good thing is that many keyboard devices are available for personal computers,
and we can use such devices for using Gear.
``Key-repeat'' feature is useful for fast scrolling of the menu.

@@

We tried various rotating devices for Gear.
Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
For example, ``jog dials''ave been widely used for controlling VCRs, and we tried the device for Gear.

(figure)

We have also tried "rollers" for Gear.
After trying these devices, we found that controlling rotating devices are not as easy as we expect,
because presice control of a hand is fairly difficult.
People are good at controling fingers, but people are usually not very good at controlling hands.

We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because
we are good at presice control of our fingers.

We can use a rotary encoder as a

@@

We used
PowerMate\footnote{
  \textsf{http://griffintechnology.com/support/powermate}
} from Griffin Technology for the rotating device.
PowerMate generates standard keyboard events when rotated,
and no special programming techniques are required.
%
Users can explore all the contents just by
rotating the device clockwise and counterclockwise.

\begin{figure}[H]
\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
\caption{A PowerMate used for the prototype.}
\label{powermate}
\end{figure}

We have also tried to use a paddle-like device for generating {\U} and {\D}.
Users can push the puddle to the right to generate {\U} and
left to generate {\D}.
Pressure sensors are installed on the puddle, and
many {\U}s are generated when the user pushs the puddle strongly.

Controling the speed of the scrolling of Gear by pressure is convenient,
since sometimes users want to jump to a far entry from current position.
That behavior is close to the key-repeat feature or computer keyboards.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1200 799]{figures/d64d2a8e1dddc57f693267f811510f23.jpg}}
\caption{Elekey.}
\label{elekey}
\end{figure}

}

@@

If we can put input devices that fits to furnituers, we can use the device near the furniture, without making the input devices look awkward.
  入力装置つきのカッコ良い家具が作れる
 If we can put the devices neatlly on furnitures and beds, people with disabilities can easilyt use them, 
 体が不自由でも使えることは間違いない

\comment{
\section*{IMPLEMENTATION}

A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
and the content is displayed in another window (Figure \ref{screenshot}).

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 671 464]{figures/95cf2fec71c52ead6fdbcb7f79aca654.png}}
\caption{Selecting an Internet radio station.}
\label{screenshot}
\end{figure}
}

\section*{DISCUSSIONS}

@@

4-way navigation is commonly used for exploring hierarchical data structure,
and it is familiar to computer users.
Some mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for choosing an item from the list and 
the push button is used for fixing the selection.
% PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
All the existing methods require more than 2 keys/buttons, and
to the best of the authors' knowledge,
Gear is the only interaction method for exploring hierarchical data structure
with one rotating device.

@@

Various information visualization techniques like
Treemap\cite{Johnson:1991:TSA:949607.949654},
Hyperbolic Tree\cite{Lamping:1995:FTB:223904.223956},
and Sunburst\cite{Stasko:2000:FDN:857190.857683}
have been proposed for visualizing large hierarchical data.
Zooming user interface (ZUI) systems like
Pad\cite{Perlin:1993:PAA:166117.166125} and
Pad++\cite{Bederson:1994:PZG:192426.192435}
can also be used for handling large hierarchical data laid out in a 2D space.
%
These visualization techniques and descendent technologies have become popular these days and
all of these systems are useful for understanding the structure of
large hierarchical data, but users of these systems have to use a pointing device
to take full advantage of their advantages.

@@

\section{Discussions}

\subsection{Is the Gear interface a new idea?}
  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
  But as far as we know, Gear is the first attempt to explore

 こういうデバイスは超簡単なので、存在した可能性はある
 特許や論文を調べた限りはみつけられなかった

\section*{EVALUATION}

>>>>

The simplest input device for Gear may be keyboards or buttons.
We tried using arrow keys on a PC, and it works fine.
Various HID devices\footnote{
  https://en.wikipedia.org/wiki/Human\_interface\_device
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  airturn pedpro
} can be used as the input device for Gear.

\begin{figure}[H]
\centerline{\includegraphics[width=40mm,bb=0 0 900 900]{figures/8d4f811f5a0c393acaff304102ba963f.jpg}}
\caption{A foot switch for turning a music score.}
\label{footswitch}
\end{figure}

%
% Good thing is that many keyboard devices are available for personal computers,
% and we can use such devices for using Gear.
% ``Key-repeat'' feature is useful for fast scrolling of the menu.

% We also tried speciial devices with pressure sensors, with which
% users can press the button strongly to simulate multiple keyboard presses.

We have also tried to use a paddle-like device for generating {\up} and {\down}.
Users can push the puddle to the right to generate {\up} and
left to generate {\down}.
Pressure sensors are installed on the puddle, and
many {\up}'s are generated when the user pushs the puddle strongly.

Controling the speed of the scrolling of Gear by pressure is convenient,
since sometimes users want to jump to a far entry from current position.
That behavior is similar to the key-repeat feature or computer keyboards.

% Keys and pressure sensors can be placed anywhere:
% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

@@

We then tried various rotating devices for Gear.
%
We tried mouse wheels first, and found that they are very suitable for Gear,
because we are good at controling fingerf precisely.

Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
For example, ``jog dials'' have been widely used for controlling VCRs, and we tried the device for Gear.

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
\caption{Using a jog dial.}
\label{jog}
\end{figure}

@@

We have also tried using a cylinder for Gear.
The cylinder shown in Figure \ref{roller} is touching the mouse wheel, and
mouse whell events are generated as the user rotates the cylinder using his arm or hand.

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
\caption{Using a roller.}
\label{roller}
\end{figure}

After trying these devices, we found that controlling rotating devices
like jog dials and cylinders are not as easy as we expected,
because presice control of an arm or a hand is fairly difficult.
People are good at controling fingers, but people are usually not very good at controlling hands.

Keys and pressure sensors can be placed anywhere:
we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1200 799]{figures/d64d2a8e1dddc57f693267f811510f23.jpg}}
\caption{Elekey.}
\label{elekey}
\end{figure}
}

@@

If we can install the devices neatlly on furnitures and beds, people with disabilities can easilyt use them,

@@

To compare the speed of Gear with conventional navigation method,
we create two applications that can check how fast a user can select an entry
from a large hierarchical database.
%
Both applicatons behaves the same way:
a user can set the date to a specific time to see a photo of a monorail from Ofuna station to Enoshima station in Japan.
%
Using the first one, a user  can set the time using Gear (Figure \ref{monorailgear}),
using {\up} and {\down} keys.

\begin{figure}[H]
\centerline{
%  \includegraphics[width=38mm,bb=0 0 1624 1193]{figures/d663e8556732d40e70e55592ca1f1258.png}
  \includegraphics[width=70mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}
}
\caption{Monorail.}
\label{monorailgeary}
\end{figure}

Using the second one, a user can set the time using the \verb+<input>+ tag of HTML (Figure \ref{monorailinput}).
Users can first set the value of the ``minute'' side using up/down keys,
and move to the ``second'' side and use up/down keys to the value of the ``second''.

\begin{figure}[H]
\centerline{
  \includegraphics[width=70mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}
}
\caption{Monorail.}
\label{monorailinput}
\end{figure}

On both applications, target time is displayed on the screen and the subjects are
asked to set the time to the displayed value.
After repeating the task 5 times, the average time is logged.

We asked 5 people to try these tasks 10 times, and the result of the experiment is
shown in Figure \ref{monorailtime}.

\begin{figure}[H]
\centerline{
  \includegraphics[width=38mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
  \includegraphics[width=38mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
}
\caption{Average time.}
\label{monorailtime}
\end{figure}

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \verb+<input>+ was 4.96s.
It takes about 40\% more time than using conventional method.

This is not 素晴らしい結果

\comment{
4-way navigation is commonly used for exploring hierarchical data structure,
and it is familiar to computer users.
Some mobile phones and PDAs are equipped with a jog dial with a push button,
where the dial is used for choosing an item from the list and 
the push button is used for fixing the selection.
% PowerMate is equipped with a push button which can used for such purposes.
% As far as we know,
All the existing methods require more than 2 keys/buttons, and
to the best of the authors' knowledge,
Gear is the only interaction method for exploring hierarchical data structure
with one rotating device.
}

@@

Various information visualization techniques like
Treemap\cite{Johnson:1991:TSA:949607.949654},
Hyperbolic Tree\cite{Lamping:1995:FTB:223904.223956},
and Sunburst\cite{Stasko:2000:FDN:857190.857683}
have been proposed for visualizing large hierarchical data.
Zooming user interface (ZUI) systems like
Pad\cite{Perlin:1993:PAA:166117.166125} and
Pad++\cite{Bederson:1994:PZG:192426.192435}
can also be used for handling large hierarchical data laid out in a 2D space.
%
These visualization techniques and descendent technologies have become popular these days and
all of these systems are useful for understanding the structure of
large hierarchical data, but users of these systems have to use a pointing device
to take full advantage of these methods.

@@

\subsection{Is the Gear interface new?}

Since the idea of Gear interface is so simple,
we have been wondering if the same idea had been around in the past.
The Gear interface had never been popular before, and
we could not find a similar method in the patent database.

こういうデバイスは超簡単なので、存在した可能性はあるが
特許や論文を調べた限りはみつけられなかった

\subsection*{Using Gear in the wild}
